Inference methods comparison for the simplified Naomi model

### 2023-03-23 src/naomi-simple_compare/comparison.Rmd
histogram_and_ecdf() generalised to work for model outputs as well #24

```{r}
pars <- unique(names(tmb$fit$obj$env$par))
pars
```

@@

## `beta_alpha`

```{r eval = pars_eval[["beta_rho"]]}
histogram_and_ecdf_helper("beta_alpha")
```

## `beta_lambda`

```{r eval = pars_eval[["beta_rho"]]}
histogram_and_ecdf_helper("beta_lambda")
```

## `beta_anc_rho`

```{r eval = pars_eval[["beta_rho"]]}
histogram_and_ecdf("beta_anc_rho")
```

## `beta_anc_alpha`

```{r eval = pars_eval[["beta_rho"]]}
histogram_and_ecdf("beta_anc_alpha")
```

## `logit`

```{r eval = FALSE}
lapply(pars[stringr::str_starts(pars, "logit")], histogram_and_ecdf)
```

## `log_sigma`

```{r eval = FALSE}
lapply(pars[stringr::str_starts(pars, "log_sigma")], histogram_and_ecdf)
```

## `u_rho_x`

```{r eval = pars_eval[["u_rho_x"]]}
histogram_and_ecdf_helper("u_rho_x")
```

## `u_rho_x`

```{r eval = pars_eval[["u_rho_x"]]}
histogram_and_ecdf_helper("u_rho_x")
```

## `us_rho_x`

```{r eval = pars_eval[["us_rho_x"]]}
histogram_and_ecdf_helper("us_rho_x")
```

## `u_rho_xs`

```{r eval = pars_eval[["u_rho_xs"]]}
histogram_and_ecdf_helper("u_rho_xs")
```

## `us_rho_xs`

```{r eval = pars_eval[["us_rho_xs"]]}
histogram_and_ecdf_helper("us_rho_xs")
```

## `u_rho_as`

```{r eval = pars_eval[["u_rho_as"]]}
histogram_and_ecdf_helper("u_rho_as")
```

## `u_alpha_x`

```{r eval = pars_eval[["u_alpha_x"]]}
histogram_and_ecdf_helper("u_alpha_x")
```

## `us_alpha_x`

```{r eval = pars_eval[["us_alpha_x"]]}
histogram_and_ecdf_helper("us_alpha_x")
```

## `u_alpha_xs`

```{r eval = pars_eval[["u_alpha_xs"]]}
histogram_and_ecdf_helper("u_alpha_xs")
```

## `us_alpha_xs`

```{r eval = pars_eval[["beta_rho"]]}
histogram_and_ecdf_helper("us_alpha_xs")
```

## `u_alpha_a`

```{r eval = pars_eval[["u_alpha_a"]]}
histogram_and_ecdf_helper("u_alpha_a")
```

## `u_alpha_as`

```{r eval = pars_eval[["u_alpha_as"]]}
histogram_and_ecdf_helper("u_alpha_as")
```

## `u_alpha_xa`

```{r eval = pars_eval[["u_alpha_xa"]]}
histogram_and_ecdf_helper("u_alpha_xa")
```

## `ui_lambda_x`

```{r eval = pars_eval[["ui_lambda_x"]]}
histogram_and_ecdf_helper("ui_lambda_x")
```

## `ui_anc_rho_x`

```{r eval = pars_eval[["ui_anc_rho_x"]]}
histogram_and_ecdf_helper("ui_anc_rho_x")
```

## `ui_anc_alpha_x`

```{r eval = pars_eval[["ui_anc_alpha_x"]]}
histogram_and_ecdf_helper("ui_anc_alpha_x")
```

## `log_or_gamma`

```{r eval = pars_eval[["log_or_gamma"]]}
histogram_and_ecdf_helper("log_or_gamma")
```

@@

```{r}
names(tmb$fit$sample)[!(names(tmb$fit$sample) %in% pars)]
```
The most important ones (checked with Jeff) are HIV prevalence (`rho_t1_out`), ART coverage (`alpha_t1_out`), and HIV incidence (`lambda_t1_out`).

@@

```{r}
histogram_and_ecdf(par = "rho_t1_out", i = 1)
```

@@

```{r}
ks_helper <- function(par, sw = FALSE, ...) {
  to_ks_df(par, starts_with = sw) %>% ks_plot(par, ...)
}
```

@@

```{r}
ks_helper("beta", sw = TRUE)
ks_helper("beta", sw = TRUE, method1 = "TMB", method2 = "adam")
```

### `logit`

```{r}
ks_helper("logit", sw = TRUE)
ks_helper("logit", sw = TRUE, method1 = "TMB", method2 = "adam")
```

### `log_sigma`

```{r}
ks_helper("log_sigma", sw = TRUE)
ks_helper("log_sigma", sw = TRUE , method1 = "TMB", method2 = "adam")
```

### `u_rho_x`

```{r eval = pars_eval[["u_rho_x"]]}
ks_helper("u_rho_x")
ks_helper("u_rho_x", method1 = "TMB", method2 = "adam")
```

### `u_rho_xs`

```{r eval = pars_eval[["u_rho_xs"]]}
ks_helper("u_rho_xs")
ks_helper("u_rho_xs", method1 = "TMB", method2 = "adam")
```

### `us_rho_x`

```{r eval = pars_eval[["us_rho_x"]]}
ks_helper("us_rho_x")
ks_helper("us_rho_x", method1 = "TMB", method2 = "adam")
```

### `us_rho_xs`

```{r eval = pars_eval[["us_rho_xs"]]}
ks_helper("us_rho_xs")
ks_helper("us_rho_xs", method1 = "TMB", method2 = "adam")
```

### `u_rho_a`

```{r eval = pars_eval[["u_rho_a"]]}
ks_helper("u_rho_a")
ks_helper("u_rho_a", method1 = "TMB", method2 = "adam")
```

### `u_rho_as`

```{r eval = pars_eval[["u_rho_as"]]}
ks_helper("u_rho_as")
ks_helper("u_rho_as", method1 = "TMB", method2 = "adam")
```

### `u_alpha_x`

```{r eval = pars_eval[["u_alpha_x"]]}
ks_helper("u_alpha_x")
ks_helper("u_alpha_x", method1 = "TMB", method2 = "adam")
```

### `u_alpha_xs`

```{r eval = pars_eval[["u_alpha_xs"]]}
ks_helper("u_alpha_xs")
ks_helper("u_alpha_xs", method1 = "TMB", method2 = "adam")
```

### `us_alpha_x`

```{r eval = pars_eval[["us_alpha_x"]]}
ks_helper("us_alpha_x")
ks_helper("us_alpha_x", method1 = "TMB", method2 = "adam")
```

### `us_alpha_xs`

```{r eval = pars_eval[["us_alpha_xs"]]}
ks_helper("us_alpha_xs")
ks_helper("us_alpha_xs", method1 = "TMB", method2 = "adam")
```

### `u_alpha_a`

```{r eval = pars_eval[["u_alpha_a"]]}
ks_helper("u_alpha_a")
ks_helper("u_alpha_a", method1 = "TMB", method2 = "adam")
```

### `u_alpha_as`

```{r eval = pars_eval[["u_alpha_as"]]}
ks_helper("u_alpha_as")
ks_helper("u_alpha_as", method1 = "TMB", method2 = "adam")
```

### `u_alpha_xa`

```{r eval = pars_eval[["u_alpha_xa"]]}
ks_helper("u_alpha_xa")
ks_helper("u_alpha_xa", method1 = "TMB", method2 = "adam")
```

### `ui_anc_rho_x`

```{r eval = pars_eval[["ui_anc_rho_x"]]}
ks_helper("ui_anc_rho_x")
ks_helper("ui_anc_rho_x", method1 = "TMB", method2 = "adam")
```

### `ui_anc_alpha_x`

```{r eval = pars_eval[["ui_anc_alpha_x"]]}
ks_helper("ui_anc_alpha_x")
ks_helper("ui_anc_alpha_x", method1 = "TMB", method2 = "adam")
```

### `log_or_gamma`

```{r eval = pars_eval[["log_or_gamma"]]}
ks_helper("log_or_gamma")
ks_helper("log_or_gamma", method1 = "TMB", method2 = "adam")
```

>>>>

```{r}
pars <- names(tmb$fit$sample)
pars
```

@@

<!-- ## `beta_alpha` -->

<!-- ```{r eval = pars_eval[["beta_rho"]]} -->
<!-- histogram_and_ecdf_helper("beta_alpha") -->
<!-- ``` -->

<!-- ## `beta_lambda` -->

<!-- ```{r eval = pars_eval[["beta_rho"]]} -->
<!-- histogram_and_ecdf_helper("beta_lambda") -->
<!-- ``` -->

<!-- ## `beta_anc_rho` -->

<!-- ```{r eval = pars_eval[["beta_rho"]]} -->
<!-- histogram_and_ecdf("beta_anc_rho") -->
<!-- ``` -->

<!-- ## `beta_anc_alpha` -->

<!-- ```{r eval = pars_eval[["beta_rho"]]} -->
<!-- histogram_and_ecdf("beta_anc_alpha") -->
<!-- ``` -->

<!-- ## `logit` -->

<!-- ```{r eval = FALSE} -->
<!-- lapply(pars[stringr::str_starts(pars, "logit")], histogram_and_ecdf) -->
<!-- ``` -->

<!-- ## `log_sigma` -->

<!-- ```{r eval = FALSE} -->
<!-- lapply(pars[stringr::str_starts(pars, "log_sigma")], histogram_and_ecdf) -->
<!-- ``` -->

<!-- ## `u_rho_x` -->

<!-- ```{r eval = pars_eval[["u_rho_x"]]} -->
<!-- histogram_and_ecdf_helper("u_rho_x") -->
<!-- ``` -->

<!-- ## `u_rho_x` -->

<!-- ```{r eval = pars_eval[["u_rho_x"]]} -->
<!-- histogram_and_ecdf_helper("u_rho_x") -->
<!-- ``` -->

<!-- ## `us_rho_x` -->

<!-- ```{r eval = pars_eval[["us_rho_x"]]} -->
<!-- histogram_and_ecdf_helper("us_rho_x") -->
<!-- ``` -->

<!-- ## `u_rho_xs` -->

<!-- ```{r eval = pars_eval[["u_rho_xs"]]} -->
<!-- histogram_and_ecdf_helper("u_rho_xs") -->
<!-- ``` -->

<!-- ## `us_rho_xs` -->

<!-- ```{r eval = pars_eval[["us_rho_xs"]]} -->
<!-- histogram_and_ecdf_helper("us_rho_xs") -->
<!-- ``` -->

<!-- ## `u_rho_as` -->

<!-- ```{r eval = pars_eval[["u_rho_as"]]} -->
<!-- histogram_and_ecdf_helper("u_rho_as") -->
<!-- ``` -->

<!-- ## `u_alpha_x` -->

<!-- ```{r eval = pars_eval[["u_alpha_x"]]} -->
<!-- histogram_and_ecdf_helper("u_alpha_x") -->
<!-- ``` -->

<!-- ## `us_alpha_x` -->

<!-- ```{r eval = pars_eval[["us_alpha_x"]]} -->
<!-- histogram_and_ecdf_helper("us_alpha_x") -->
<!-- ``` -->

<!-- ## `u_alpha_xs` -->

<!-- ```{r eval = pars_eval[["u_alpha_xs"]]} -->
<!-- histogram_and_ecdf_helper("u_alpha_xs") -->
<!-- ``` -->

<!-- ## `us_alpha_xs` -->

<!-- ```{r eval = pars_eval[["beta_rho"]]} -->
<!-- histogram_and_ecdf_helper("us_alpha_xs") -->
<!-- ``` -->

<!-- ## `u_alpha_a` -->

<!-- ```{r eval = pars_eval[["u_alpha_a"]]} -->
<!-- histogram_and_ecdf_helper("u_alpha_a") -->
<!-- ``` -->

<!-- ## `u_alpha_as` -->

<!-- ```{r eval = pars_eval[["u_alpha_as"]]} -->
<!-- histogram_and_ecdf_helper("u_alpha_as") -->
<!-- ``` -->

<!-- ## `u_alpha_xa` -->

<!-- ```{r eval = pars_eval[["u_alpha_xa"]]} -->
<!-- histogram_and_ecdf_helper("u_alpha_xa") -->
<!-- ``` -->

<!-- ## `ui_lambda_x` -->

<!-- ```{r eval = pars_eval[["ui_lambda_x"]]} -->
<!-- histogram_and_ecdf_helper("ui_lambda_x") -->
<!-- ``` -->

<!-- ## `ui_anc_rho_x` -->

<!-- ```{r eval = pars_eval[["ui_anc_rho_x"]]} -->
<!-- histogram_and_ecdf_helper("ui_anc_rho_x") -->
<!-- ``` -->

<!-- ## `ui_anc_alpha_x` -->

<!-- ```{r eval = pars_eval[["ui_anc_alpha_x"]]} -->
<!-- histogram_and_ecdf_helper("ui_anc_alpha_x") -->
<!-- ``` -->

<!-- ## `log_or_gamma` -->

<!-- ```{r eval = pars_eval[["log_or_gamma"]]} -->
<!-- histogram_and_ecdf_helper("log_or_gamma") -->
<!-- ``` -->

@@

```{r}
names(tmb$fit$sample)[!(names(tmb$fit$sample) %in% unique(names(tmb$fit$obj$env$par)))]
```
The most important ones (checked with Jeff) are HIV prevalence (`rho_t1_out`), ART coverage (`alpha_t1_out`), and HIV incidence (`lambda_t1_out`).

@@

Something weird happening with `adam`, go back and check this:

```{r}
histogram_and_ecdf(par = "alpha_t1_out", i = 1)
```

@@

```{r}
ks_helper <- function(par, starts_with = FALSE, ...) {
  to_ks_df(par, starts_with = starts_with) %>% ks_plot(par, ...)
}
```

@@

```{r}
ks_helper("beta", starts_with = TRUE)
ks_helper("beta", starts_with = TRUE, method1 = "TMB", method2 = "adam")
```

<!-- ### `logit` -->

<!-- ```{r} -->
<!-- ks_helper("logit", starts_with = TRUE) -->
<!-- ks_helper("logit", starts_with = TRUE, method1 = "TMB", method2 = "adam") -->
<!-- ``` -->

<!-- ### `log_sigma` -->

<!-- ```{r} -->
<!-- ks_helper("log_sigma", starts_with = TRUE) -->
<!-- ks_helper("log_sigma", starts_with = TRUE , method1 = "TMB", method2 = "adam") -->
<!-- ``` -->

<!-- ### `u_rho_x` -->

<!-- ```{r eval = pars_eval[["u_rho_x"]]} -->
<!-- ks_helper("u_rho_x") -->
<!-- ks_helper("u_rho_x", method1 = "TMB", method2 = "adam") -->
<!-- ``` -->

<!-- ### `u_rho_xs` -->

<!-- ```{r eval = pars_eval[["u_rho_xs"]]} -->
<!-- ks_helper("u_rho_xs") -->
<!-- ks_helper("u_rho_xs", method1 = "TMB", method2 = "adam") -->
<!-- ``` -->

<!-- ### `us_rho_x` -->

<!-- ```{r eval = pars_eval[["us_rho_x"]]} -->
<!-- ks_helper("us_rho_x") -->
<!-- ks_helper("us_rho_x", method1 = "TMB", method2 = "adam") -->
<!-- ``` -->

<!-- ### `us_rho_xs` -->

<!-- ```{r eval = pars_eval[["us_rho_xs"]]} -->
<!-- ks_helper("us_rho_xs") -->
<!-- ks_helper("us_rho_xs", method1 = "TMB", method2 = "adam") -->
<!-- ``` -->

<!-- ### `u_rho_a` -->

<!-- ```{r eval = pars_eval[["u_rho_a"]]} -->
<!-- ks_helper("u_rho_a") -->
<!-- ks_helper("u_rho_a", method1 = "TMB", method2 = "adam") -->
<!-- ``` -->

<!-- ### `u_rho_as` -->

<!-- ```{r eval = pars_eval[["u_rho_as"]]} -->
<!-- ks_helper("u_rho_as") -->
<!-- ks_helper("u_rho_as", method1 = "TMB", method2 = "adam") -->
<!-- ``` -->

<!-- ### `u_alpha_x` -->

<!-- ```{r eval = pars_eval[["u_alpha_x"]]} -->
<!-- ks_helper("u_alpha_x") -->
<!-- ks_helper("u_alpha_x", method1 = "TMB", method2 = "adam") -->
<!-- ``` -->

<!-- ### `u_alpha_xs` -->

<!-- ```{r eval = pars_eval[["u_alpha_xs"]]} -->
<!-- ks_helper("u_alpha_xs") -->
<!-- ks_helper("u_alpha_xs", method1 = "TMB", method2 = "adam") -->
<!-- ``` -->

<!-- ### `us_alpha_x` -->

<!-- ```{r eval = pars_eval[["us_alpha_x"]]} -->
<!-- ks_helper("us_alpha_x") -->
<!-- ks_helper("us_alpha_x", method1 = "TMB", method2 = "adam") -->
<!-- ``` -->

<!-- ### `us_alpha_xs` -->

<!-- ```{r eval = pars_eval[["us_alpha_xs"]]} -->
<!-- ks_helper("us_alpha_xs") -->
<!-- ks_helper("us_alpha_xs", method1 = "TMB", method2 = "adam") -->
<!-- ``` -->

<!-- ### `u_alpha_a` -->

<!-- ```{r eval = pars_eval[["u_alpha_a"]]} -->
<!-- ks_helper("u_alpha_a") -->
<!-- ks_helper("u_alpha_a", method1 = "TMB", method2 = "adam") -->
<!-- ``` -->

<!-- ### `u_alpha_as` -->

<!-- ```{r eval = pars_eval[["u_alpha_as"]]} -->
<!-- ks_helper("u_alpha_as") -->
<!-- ks_helper("u_alpha_as", method1 = "TMB", method2 = "adam") -->
<!-- ``` -->

<!-- ### `u_alpha_xa` -->

<!-- ```{r eval = pars_eval[["u_alpha_xa"]]} -->
<!-- ks_helper("u_alpha_xa") -->
<!-- ks_helper("u_alpha_xa", method1 = "TMB", method2 = "adam") -->
<!-- ``` -->

<!-- ### `ui_anc_rho_x` -->

<!-- ```{r eval = pars_eval[["ui_anc_rho_x"]]} -->
<!-- ks_helper("ui_anc_rho_x") -->
<!-- ks_helper("ui_anc_rho_x", method1 = "TMB", method2 = "adam") -->
<!-- ``` -->

<!-- ### `ui_anc_alpha_x` -->

<!-- ```{r eval = pars_eval[["ui_anc_alpha_x"]]} -->
<!-- ks_helper("ui_anc_alpha_x") -->
<!-- ks_helper("ui_anc_alpha_x", method1 = "TMB", method2 = "adam") -->
<!-- ``` -->

<!-- ### `log_or_gamma` -->

<!-- ```{r eval = pars_eval[["log_or_gamma"]]} -->
<!-- ks_helper("log_or_gamma") -->
<!-- ks_helper("log_or_gamma", method1 = "TMB", method2 = "adam") -->
<!-- ``` -->

### Outcome variables

```{r}
# To fix
# ks_helper("alpha_t1_out")
```
